---
title: "Rent-Price Ratio Comparison"
author: "Andy Krause and Gideon Aschwanden"
date: "March 21, 2016"
output: html_document
---

This document describes the process taken to create the results of the rent-price ratio comparison working paper.  The analysis is conducted in R.  All code can be found at the project's [github page](https://github.com/andykrause/ausPropMrkt).

### Preliminary commands

We begin with a set of preliminary commands such as setting basic parameters, sourcing files, reading in libraries, etc.  

#### Basic Control Parameters

There are four basic (and binary) control parameters.  The parameter determine a number of the actions takes, the level of feedback given and the location from which to source files.  

1. **reBuildData** determines whether or not to rebuild the data from the raw datasets or to load a pre-cleaned data object.
2. **reAnalyze** determines whether or not to re-analyze and re-calculate the individual yield estimates at the geographic and property levels.  
3. **offline** if you are offline, then this will source the necessary code files from a local directory
4. **verbose** sets whether or not to return progress outputs from larger functions

```{r, echo=TRUE}
  reBuildData <- FALSE
  reAnalyze <- FALSE
  offline <- FALSE
  verbose <- TRUE
```

It should be noted that more specific parameters, such as those consider in data cleaning and preparation exercises are set at by the *_apmSetOptions()_* which is shown below.  Options are stored in the **apmOptions** object in the global environment and can be changed with *_apmChgOptions()_*.  

#### Paths to Data

Next, we set the path to the various data directories and specific files.  

1. **data.path** is the general path to data directory
2. **export.path** is the path to export specific data and images to
3. **sale.file** is the specific location and name of the sales file within the **data.path**
4. **rent.file** is the specfic location and name of the rentals file within the **data.path**
5. **geo.path**

```{r, echo=TRUE}
  dataPath <- "C:/data/research/priceRentMethComp/"
  exportPath <- dataPath
  salePath <- 'transData/newSales.csv'
  rentPath <- 'transData/newRentals.csv'
  geoPath=list(suburb='shapefiles/Vic_Suburbs.shp',
               lga='shapefiles/Vic_LGAs.shp',
               sla1='shapefiles/Vic_SLA1.shp',
               postcode='shapefiles/Vic_PostCodes.shp',
               ssFile='spatialData/allSS.csv')
  
```  
  
  
  
  
  
  
  